\documentclass[a4paper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[colorlinks=true, urlcolor=blue, linkcolor=blue]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[top=0.15in, bottom=0.15in, left=0.25in, right=0.25in]{geometry}
\usepackage{ragged2e}
\usepackage{graphicx}
\input{glyphtounicode}

% Font options
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-12pt}\scshape\raggedright\large\color{blue}
}{}{0em}{}[\color{blue}\titlerule \vspace{-4pt}]
 
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}, itemsep=-1pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[itemsep=0pt, parsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADER----------
\begin{center}
    {\color{blue}\textbf{\huge \scshape Thulasimanikandan M}} \\ \vspace{1pt}
    \small 7305371881 $|$ \href{mailto:thulasitmk181@gmail.com}{\color{black}thulasitmk181@gmail.com} $|$ Dharapuram, Tirupur \\ \vspace{1pt}
    {\color{blue}
    \href{https://www.linkedin.com/in/thulasimanikandan-m-508556292}{LinkedIn} $|$
    \href{https://github.com/THULASI18MANIKANDAN}{GitHub} $|$
    \href{https://leetcode.com/u/nWkrDSKPwf/}{LeetCode}}
\end{center}


%----------SUMMARY----------
\section{Summary}
{\justify
\small AI \& Full-Stack Developer skilled in Python, Java, and MERN stack with hands-on experience building scalable web applications and deep learning models. Strong in DSA and backend architecture with practical experience in REST APIs and real-time systems. Passionate about solving real-world problems through intelligent software systems. \par
}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {KPR Institute of Engineering and Technology}{Coimbatore, India}
      {Bachelor of Technology in Artificial Intelligence and Data Science}{2023 -- 2027}
      \resumeItemListStart
      \resumeItem{CGPA: 8.15 / 10}
      \resumeItemListEnd
      
    \resumeSubheading
      {NV Matriculation Higher Secondary School}{Tiruppur, India}
      {Computer Science}{2021 -- 2023}
      \resumeItemListStart
      \resumeItem{Percentage: 92.3 / 100}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Mist Solutions}{Jan 2025}
      {Internship Trainee}{}
      \resumeItemListStart
        \resumeItem{Developed responsive e-commerce website improving UI usability and performance.}
        \resumeItem{Implemented modular frontend components using Bootstrap and JavaScript. }
      \resumeItemListEnd

    \resumeSubheading
      {GradTwin Services Private Limited}{July 2025}
      {Backend Python Developer}{}
      \resumeItemListStart
        \resumeItem{Completed a 15-day internship at GradTwin as a Backend Python Developer Intern.}
        \resumeItem{Built a complete Car Rental System using Flask  with frontend integration in HTML, CSS, and JavaScript.}
        \resumeItem{Gained hands-on experience in Python core modules, RESTful API development, and end-to-end application deployment.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}, itemsep=-2pt]
    \small{\item{
     \textbf{Programming Languages}{: Python, Java} \\
     \textbf{Frontend}{: HTML, CSS, JavaScript, React.js,React Native(basics)} \\
     \textbf{Backend}{: Flask, Node.js} \\
     \textbf{Databases}{: MySQL, MongoDB} \\
     \textbf{Frameworks \& Libraries}{: Numpy, Pandas, Streamlit, OpenCV} \\
     \textbf{Tools}{: Figma, VS Code, Github,Expo Go}
    }}
 \end{itemize}


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{Car Rental System} $|$ \emph{Flask, SQLite, HTML, CSS, JavaScript} $|$ 
          \href{https://github.com/THULASI18MANIKANDAN/car-booking-app}{Link}}{}
          \resumeItemListStart
            \resumeItem{Built a full-stack car rental web application with user authentication,session management,and real-time car availability tracking.}
            \resumeItem{Implemented an admin dashboard for managing cars, users,and bookings,including rental/return workflows and secure password handling.}
            \resumeItem{Designed a responsive interface with modern styling for an enhanced user experience.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Digitalized Central Platform for Alumni Engagement} $|$ \emph{MongoDB, Express.js, React.js, Node.js} $|$
          \href{https://github.com/THULASI18MANIKANDAN/Alumni-Engagement-platform}{Link}}{}
          \resumeItemListStart
            \resumeItem{Developed a centralized alumni engagement platform to streamline networking, mentorship, and career opportunities between students, alumni, and administrators.}
            \resumeItem{Implemented secure login, profile management, job/event postings, and real-time communication.}
            \resumeItem{Built an admin dashboard for alumni data oversight and content moderation, ensuring scalability and user-friendly access.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Deepfake Analyzer} $|$ \emph{Python, Flask, TensorFlow, PyTorch, OpenCV} $|$
          \href{https://github.com/THULASI18MANIKANDAN/deepfake_analyser}{Link}}{}
          \resumeItemListStart
            \resumeItem{Developed a Deepfake Analyzer capable of detecting manipulated videos using advanced deep learning techniques (TensorFlow/Keras, PyTorch).}
            \resumeItem{Integrated Flask APIs for seamless backend deployment and real-time video analysis.}
            \resumeItem{Built a responsive web interface using HTML, CSS, and Bootstrap/Tailwind, providing accurate predictions on video authenticity.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------KEY ACHIEVEMENTS-----------
\vspace{-10pt}\section{Key Achievements}
  \resumeSubHeadingListStart
    \resumeItem{\textbf{Line Follower Event}: Won First Prize in the Line Follower Robotics Event at Anna University, showcasing expertise in automation, problem-solving, and robotics development.}
    \resumeItem{\textbf{Best Student Volunteer}: Awarded "Best Student Volunteer" by SPARKS Association for outstanding contribution in organizing and managing a college-level hackathon event.}
  \resumeSubHeadingListEnd
%-----------CERTIFICATIONS-----------
\section{Certifications}
  \resumeSubHeadingListStart
    \resumeItem{Data Analytics With Python - NPTEL}
    \resumeItem{Practical Cyber Security for Cyber Security Practitioners - NPTEL}
    \resumeItem{Node.js - Linux Foundation}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
